Analysis

### 2018-06-26 reports/analysis_pilot.Rmd
add pilot data

@@

@@

>>>>

```{r, warning=FALSE}

@@

df <- data_pth %>% 
  dir(pattern = "*.csv", full.names = T) %>% 
  purrr::map(read_csv, col_types = col_types) %>% 
  bind_rows()

@@

df %>% 
  group_by(category) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2), n= n()) %>% 
  arrange(-m)

df %>% 
  group_by(category,quintile) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2), n= n()) %>% 
  arrange(category,-m)
